Exploration

### 2018-03-01 exploration.Rmd
added seedbank for theoretical and simulation version; IPMpack still to do

## Species description: Life history, characteristics, relevant attributes
The simulated species is fully described here. The object `sp_i` is a list containing elements for the global parameters, relationships with environmental variables, and demographic matrices that are applicable or potentially applicable for that modeling strategy. Parameters are abbreviated with the associated kernel component (e.g., `s_` for survival, `g_` for growth, etc) and the type of covariate (`_z` for size, `_x` for environmental covariates).
```{r sp_i}
set.seed(20)
subsamp <- 100
mean_abund <- 2000
regPlots <- F
ipmPlots <- F
if(is.na(subsamp)) { cells <- 1:n_distinct(lc.df$CellID)
} else { cells <- sample(1:n_distinct(lc.df$CellID), subsamp, replace=FALSE) }
n.cell <- length(cells)
n_i <- rpois(n.cell, mean_abund)
sp_i <- list(p=list(s_z=c(-4, .75), # b1 + b2*z
                    s_x=c(-1, -.1, 1, -.1), # b1*x1 + ...
                    g_z=c(.2, 2, -0.1), # b1 + b2*z + b3*z^2
                    g_x=c(-1, -.1, 1, -.1), #b1*x1 + ...
                    g_sig=1, # N(E, sig)
                    fl_z=c(-7.5, 1.2, -.2, .1), # b1 + b2*z + b3*z^2
                    fl_x=c(-1, -.01, 1, -.01), # b1*x1 + ...
                    seed_z=c(2, 0.5, -.03), # b1 + b2*z
                    seed_x=c(-1, -.1, 1, -.1), # b1*x1 + ...
                    rcrt=c(1.5, 0.4), #N(mean=rcrt1, sd=rcrt2)
                    p_est=0.02))
```

@@

## Simulation: IPM framework
```{r S}
########
## set up
########
# set up storage objects
p <- sp_i$p
d <- vector("list", length=n.cell)
lambdas <- lambdas2 <- rep(NA, n.cell)

@@

# life history functions
z_pow <- function(z.vec, n_z) {
  if(n_z==1) {
    return(matrix(1, ncol=1, nrow=length(z.vec)))
  } else {
    z <- matrix(z.vec, nrow=length(z.vec), ncol=n_z-1)
    for(i in 1:(n_z-1)) z[,i] <- z[,i]^i
    z <- cbind(1, z)
    return(z)
  }
}
calc_surv <- function(z.v, n_sz, p, X.s) {
  z <- z_pow(z.v, n_sz)
  u <- exp(z %*% p$s_z + c(t(X.s) %*% p$s_x))
  return(u / (1+u))
}
calc_grow <- function(z1, z.v, n_gz, p, X.g) {
  z <- z_pow(z.v, n_gz)
  g <- dnorm(z1, mean=z %*% p$g_z + c(t(X.g) %*% p$g_x), 
             sd=p$g_sig)
  return(g)
}
calc_flwr <- function(z.v, n_flz, p, X.fl) {
  z <- z_pow(z.v, n_flz)
  u <- exp(z %*% p$fl_z + c(t(X.fl) %*% p$fl_x))
  return(u / (1+u))
}
calc_seed <- function(z1, z.v, n_seedz, n_flz, p, X.seed, X.fl) {
  z <- z_pow(z.v, n_seedz)
  calc_flwr(z.v, n_flz, p, X.fl) * p$p_est *
      dnorm(z1, p$rcrt[1], p$rcrt[2]) *
      exp(z %*% p$seed_z + c(t(X.seed) %*% p$seed_x))
}

@@

  ## seed production
  E_seed <- d[[i]]$fl * exp((size.mx[,1:n_seedz] %*% p$seed_z + 
                               c(X_seed[i,] %*% p$seed_x)))
  d[[i]]$seed <- rpois(n_i[i], E_seed)
  d[[i]]$seed <- ifelse(d[[i]]$fl, d[[i]]$seed, 0)
  seed.range <- range(d[[i]]$seed, na.rm=TRUE)

  ## recruits
  rcrt.n <- max(sum(d[[i]]$seed, na.rm=TRUE)*p$p_est, 1)
  rcrt.i <- (n_i[i]+1):(n_i[i]+rcrt.n)
  d[[i]][rcrt.i,] <- NA
  d[[i]]$sizeNext[rcrt.i] <- rnorm(rcrt.n, p$rcrt[1], p$rcrt[2])

  # fill IPM matrices
  ## Manual: use assigned slopes
  n <- 50  # ncells in matrix
  b <- lo + c(0:n)*(hi - lo)/n  # boundary points
  y <- 0.5*(b[1:n] + b[2:(n+1)])  # mesh points
  h <- y[2] - y[1]  # step size

  G.mx <- h*outer(y, y, calc_grow, n_gz=n_gz, p=p, X.g=X_g[i,])
  S.v <- calc_surv(y, n_sz, p, X_s[i,])
  F.mx <- h*outer(y, y, calc_seed, n_seedz=n_seedz, p=p, n_flz=n_flz,
                  X.seed=X_seed[i,], X.fl=X_fl[i,])
  P.mx <- G.mx
  for(k in 1:(n/2)) { # Fix eviction of individuals below/above size limits
    G.mx[1,k] <- G.mx[1,k] + 1 - sum(G.mx[,k])
    P.mx[,k] <- G.mx[,k]*S.v[k]
  }
  for(k in (n/2+1):n) {
    G.mx[n,k] <- G.mx[n,k] + 1 - sum(G.mx[,k])
    P.mx[,k] <- G.mx[,k]*S.v[k]
  }
  IPM <- P.mx + F.mx

  ## IPMpack: estimate slopes from d[[i]]
  so <- makeSurvObj(d[[i]], surv ~ size)
  go <- makeGrowthObj(d[[i]], sizeNext ~ size + size2)
  fo <- makeFecObj(d[[i]],
                   Formula=c(fl~size+size2+size3, seed~size),
                   Family=c("binomial", "poisson"),
                   Transform=c("none", "none"))
  P.mx2 <- makeIPMPmatrix(growObj=go, survObj=so, minSize=lo, maxSize=hi,
                         correction="constant")
  F.mx2 <- makeIPMFmatrix(fecObj=fo, minSize=lo, maxSize=hi,
                          correction="constant")
  IPM2 <- P.mx2 + F.mx2
  lambdas[i] <- Re(eigen(IPM)$values[1])
  lambdas2[i] <- Re(eigen(IPM2)$values[1])

  # Plots
  z.t <- d[[i]][!is.na(d[[i]]$size),]; main.i <- paste("Cell", i)
  if(regPlots) {
    par(mfrow=c(3,2), mar=c(4,4,2,1))
    plot(surv~size, data=d[[i]], ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      points(z.t$size, E_surv, cex=0.1, col="red")
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), 
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      points(z.t$size, E_grow, cex=0.1, col="red")
      abline(a=0, b=1, col="blue", lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower:", main.i), xlab="Size (t)", ylab="P(flower)")
      points(z.t$size, E_fl, cex=0.1, col="red")
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      points(z.t$size, E_seed, cex=0.1, col="red")
    w1 <- Re(eigen(IPM)$vectors[,1]); stable.dist1 <- w1/sum(w1)
    w2 <- Re(eigen(IPM2)$vectors[,1]); stable.dist2 <- w2/sum(w2)
    plot(y, stable.dist1, ylab="", type="l", lwd=2,
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    lines(y, stable.dist2, lwd=2, lty=2)
    # plot(y, S.v); points(y, apply(P.mx, 2, sum), col="red", type="l")
    hist(d[[i]]$sizeNext[rcrt.i], main=paste("Recruit sizes:", main.i), 
         xlab="Recruit size (t+1)", col="grey", freq=FALSE)
      xx <- seq(0, hi*.5, length.out=100)
      lines(xx, dnorm(xx, p$rcrt[1], p$rcrt[2]), col="red")
  }
  if(ipmPlots) {
    par(mfrow=c(2,2), mar=c(4,4,2,1)); main.i <- paste("Cell", i)
    # sens.mx <- sens(IPM2); elas.mx <- elas(IPM2)
    sens.mx <- sens(IPM); elas.mx <- elas(IPM)
    image.plot(y, y, t(P.mx), main=main.i, xlab="Size (t)", ylab="Size (t+1)")
    points(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2))
    abline(a=0, b=1, col="white", lty=2)
    image.plot(y, y, t(P.mx2), main=main.i, xlab="Size (t)", ylab="Size (t+1)")
      points(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2))
      abline(a=0, b=1, col="white", lty=2)
    image.plot(1:dim(sens.mx)[1], 1:dim(sens.mx)[1], t(sens.mx),
               main=paste("Sens:", main.i), xlab="Size (t)", ylab="Size (t+1)")
    image.plot(1:dim(elas.mx)[1], 1:dim(elas.mx)[1], t(elas.mx),
               main=paste("Elas:", main.i), xlab="Size (t)", ylab="Size (t+1)")
  }
  if(i %% 100 == 0) cat("Finished cell", i, "\n")
}
lam.df <- env.df %>% add_column(lambda=lambdas, lambda2=lambdas2)
ggplot(lam.df, aes(x=x, y=y, fill=log(lambdas))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", midpoint=0)
par(mfrow=c(2,2))
plot(lambdas ~ temp, data=lam.df, log="y")
plot(lambdas ~ prec, data=lam.df, log="y")
plot(lambdas, lambdas2)
plot(density(log(lambdas))); abline(v=0, col="red", lty=2)
```

>>>>

## Species description: Life history, characteristics, relevant attributes
The simulated species is fully described here. The object `sp_i` is a list containing elements for the global parameters, relationships with environmental variables, and demographic matrices that are applicable or potentially applicable for that modeling strategy. Parameters are abbreviated with the associated kernel component (e.g., `s_*` for survival, `g_*` for growth, etc) and the type of covariate (`*_z` for size, `*_x` for environmental covariates).
```{r sp_i}
#set.seed(20)
subsamp <- NA
mean_abund <- 500
regPlots <- F
ipmPlots <- F
if(is.na(subsamp)) { cells <- 1:n_distinct(lc.df$CellID)
} else { cells <- sample(1:n_distinct(lc.df$CellID), subsamp, replace=FALSE) }
n.cell <- length(cells)
n_i <- rpois(n.cell, mean_abund)
sp_i <- list(p=list(s_z=c(-1.75, .75), # b1 + b2*z
                    s_x=c(1, -.1, -.5, -.1), # b1*x1 + ...
                    g_z=c(.2, 2, -0.1), # b1 + b2*z + b3*z^2
                    g_x=c(1, -.1, 1.5, -.1), #b1*x1 + ...
                    g_sig=1, # growth ~ N(E, g_sig)
                    fl_z=c(-1.5, .1, .1), # b1 + b2*z + b3*z^2 + b4*z^3
                    fl_x=c(1, -.01, -1, -.01), # b1*x1 + ...
                    seed_z=c(2, 0.5, -.03), # b1 + b2*z + b2*z^2
                    seed_x=c(1, -.1, 1, -.1), # b1*x1 + ...
                    rcr_z=c(1.5, 0.4), # N(mean=rcrt1, sd=rcrt2)
                    p_est=0.02, # p(establishment)
                    rcr_SB=0.4, # p(recruit from seedbank)
                    rcr_dir=0.5, # p(recruit directly)
                    s_SB=0.3 # p(survive in seedbank additional year)
                    ))
```

@@

## Simulation: IPM framework
```{r S}
########
## set up
########
# set up storage objects
p <- sp_i$p
d <- vector("list", length=n.cell)
lambdas <- lambdas2 <- B_1 <- rep(NA, n.cell)
B <- rpois(n.cell, n_i)

@@

# life history functions
z_pow <- function(z.vec, n_z) {
  if(n_z==1) {
    return(matrix(1, ncol=1, nrow=length(z.vec)))
  } else {
    z <- matrix(z.vec, nrow=length(z.vec), ncol=n_z-1)
    for(i in 1:(n_z-1)) z[,i] <- z[,i]^i
    z <- cbind(1, z)
    return(z)
  }
}
calc_surv <- function(z.v, p, n_sz, X.s) {
  z <- z_pow(z.v, n_sz)
  u <- exp(z %*% p$s_z + c(t(X.s) %*% p$s_x))
  return(u / (1+u))
}
calc_grow <- function(z1, z.v, p, n_gz, X.g) {
  z <- z_pow(z.v, n_gz)
  g <- dnorm(z1, mean=z %*% p$g_z + c(t(X.g) %*% p$g_x), 
             sd=p$g_sig)
  return(g)
}
calc_flwr <- function(z.v, p, n_flz, X.fl) {
  z <- z_pow(z.v, n_flz)
  u <- exp(z %*% p$fl_z + c(t(X.fl) %*% p$fl_x))
  return(u / (1+u))
}
calc_rcrDir <- function(z1, z.v, p, n_seedz, n_flz, X.seed, X.fl) {
  z <- z_pow(z.v, n_seedz)
  calc_flwr(z.v, p, n_flz, X.fl) *
    exp(z %*% p$seed_z + c(t(X.seed) %*% p$seed_x)) *
    p$rcr_dir * 
    p$p_est * 
    dnorm(z1, p$rcr_z[1], p$rcr_z[2])
}
calc_rcrSB <- function(z1, p) {
  p$s_SB * dnorm(z1, p$rcr_z[1], p$rcr_z[2])
}
calc_addSB <- function(z.v, p, n_seedz, n_flz, X.seed, X.fl) {
  z <- z_pow(z.v, n_seedz)
  calc_flwr(z.v, p, n_flz, X.fl) *
    exp(z %*% p$seed_z + c(t(X.seed) %*% p$seed_x)) *
    (1 - p$rcr_dir) *
    p$s_SB
}
calc_staySB <- function(p) {
  p$s_SB * (1 - p$rcr_SB)
}

@@

  ## seed production
  E_seed <- d[[i]]$fl * exp((size.mx[,1:n_seedz] %*% p$seed_z 
                             + c(X_seed[i,] %*% p$seed_x)))
  d[[i]]$seed <- rpois(n_i[i], E_seed)
  d[[i]]$fl <- ifelse(d[[i]]$surv, d[[i]]$fl, NA)
  d[[i]]$seed <- ifelse(d[[i]]$fl==1, d[[i]]$seed, NA)

  ## seed bank
  B_1[i] <- B[i] * p$s_SB * (1 - p$rcr_SB) + 
    sum(d[[i]]$seed, na.rm=TRUE) * (1 - p$rcr_dir) * p$s_SB

  ## recruits
  rcrt.n <- max((sum(d[[i]]$seed, na.rm=TRUE) * p$rcr_dir +
                   B[i] * p$rcr_SB) * p$p_est, 
                2) # need ≥ 2 for IPMpack estimate of rcr_z'_mn, rcr_z'_sd
  rcrt.i <- (n_i[i]+1):(n_i[i]+rcrt.n)
  d[[i]][rcrt.i,] <- NA
  d[[i]]$sizeNext[rcrt.i] <- rnorm(rcrt.n, p$rcr_z[1], p$rcr_z[2])

  # fill IPM matrices
  ## Manual: use assigned slopes
  n <- 50  # ncells in matrix
  b <- lo + c(0:n)*(hi - lo)/n  # boundary points
  y <- 0.5*(b[1:n] + b[2:(n+1)])  # mesh points
  h <- y[2] - y[1]  # step size
  ### growth and survival
  G.mx <- h*outer(y, y, calc_grow, p=p, n_gz=n_gz, X.g=X_g[i,])
  S.v <- calc_surv(y, p=p, n_sz=n_sz, X.s=X_s[i,])
  ### Fix eviction of individuals below/above size limits
  for(k in 1:(n/2)) G.mx[1,k] <- G.mx[1,k] + 1 - sum(G.mx[,k])
  for(k in (n/2+1):n) G.mx[n,k] <- G.mx[n,k] + 1 - sum(G.mx[,k])
  ### fill P matrix
  P.mx <- F.mx <- matrix(0, ncol=n+1, nrow=n+1)
  for(k in 2:(n+1)) P.mx[k,2:(n+1)] <- G.mx[k-1,]*S.v
  P.mx[1,1] <- calc_staySB(p)

  ### fecundity
  F.mx[2:(n+1), 2:(n+1)] <- h*outer(y, y, calc_rcrDir, p=p, 
                                    n_seedz=n_seedz, n_flz=n_flz, 
                                    X.seed=X_seed[i,], X.fl=X_fl[i,])
  F.mx[1,2:(n+1)] <- calc_addSB(y, p=p, n_seedz=n_seedz, n_flz=n_flz, 
                                X.seed=X_seed[i,], X.fl=X_fl[i,])
  F.mx[2:(n+1),1] <- calc_rcrSB(y, p)

  ### final K
  IPM <- P.mx + F.mx

  # ## IPMpack: estimate slopes from d[[i]]
  # ### set up seedbank transitions
  # d[[i]]$stage <- d[[i]]$stageNext <- "continuous"
  # d[[i]]$stage[is.na(d[[i]]$size)] <- NA
  # d[[i]]$stageNext[d[[i]]$surv==0] <- "dead"
  # d[[i]]$number <- 1 
  # seedbank <- data.frame(size=NA, surv=1, sizeNext=NA,
  #                        fl=NA, seed=NA, 
  #                        stage=c("seedbank", "seedbank", "continuous"),
  #                        stageNext=c("seedbank", "continuous", "seedbank"),
  #                        number=c(p$s_SB, p$rcr_SB*p$p_est, (1-p$rcr_dir)))
  # d[[i]] <- rbind(d[[i]], seedbank)
  # d[[i]]$stage <- as.factor(d[[i]]$stage)
  # d[[i]]$stageNext <- as.factor(d[[i]]$stageNext)
  ### construct kernels
  so <- makeSurvObj(d[[i]], surv ~ size)
  go <- makeGrowthObj(d[[i]], sizeNext ~ size + size2)
  fo <- makeFecObj(d[[i]],
                   Formula=c(fl~size+size2, seed~size+size2),
                   Family=c("binomial", "poisson"),
                   Transform=c("none", "none"),
                   # meanOffspringSize=mean(
                   #   d[[i]]$sizeNext[is.na(d[[i]]$size) &
                   #                     !is.na(d[[i]]$sizeNext)]),
                   # sdOffspringSize=sd(
                   #   d[[i]]$sizeNext[is.na(d[[i]]$size) &
                   #                     !is.na(d[[i]]$sizeNext)]),
                   fecConstants=data.frame(seedlingEstablishmentRate=p$p_est)#,
                   # offspringSplitter=data.frame(seedbank=(1-p$rcr_dir),
                   #                              continuous=p$rcr_dir)
                   )
  F.mx2 <- makeIPMFmatrix(fecObj=fo, minSize=lo, maxSize=hi,
                          correction="constant")
  # D.mx2 <- makeDiscreteTrans(d[[i]])
  # dummy <- as.matrix(fo@offspringRel$coefficients[1], list(1, "seedbank"))
  # D.mx2@meanToCont <- as.matrix(dummy, dimnames=c(1, "seedbank"))
  # dummy <- as.matrix(fo@sdOffspringSize, dimnames=list(1, "seedbank"))
  # D.mx2@sdToCont <- as.matrix(dummy, dimnames=c(1, "seedbank"))
  # D.mx2@discreteTrans[1,1] <- p$s_SB 
  # D.mx2@discreteTrans[3,1] <- 1 - sum(D.mx2@discreteTrans[1:2,1])
  P.mx2 <- makeIPMPmatrix(growObj=go, survObj=so, #discreteTrans=D.mx2,
                            minSize=lo, maxSize=hi, correction="constant")
  IPM2 <- P.mx2 + F.mx2

  lambdas[i] <- Re(eigen(IPM)$values[1])
  lambdas2[i] <- Re(eigen(IPM2)$values[1])

  # Plots
  z.t <- d[[i]][!is.na(d[[i]]$size),]; main.i <- paste("Cell", i)
  if(regPlots) {
    par(mfrow=c(3,2), mar=c(4,4,2,1))
    xx <- tibble(size=seq(lo, hi, length.out=100), size2=size^2, size3=size^3)
    plot(surv~size, data=d[[i]], ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      points(z.t$size, E_surv, cex=0.2, col="red")
      lines(xx$size, predict(so@fit, xx, type="response"), col="blue")
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), 
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      points(z.t$size, E_grow, cex=0.2, col="red")
      lines(xx$size, predict(go@fit, xx, type="response"), col="blue")
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      points(z.t$size, E_fl, cex=0.2, col="red")
      lines(xx$size, predict(fo@fitFec[[1]], xx, type="response"), col="blue")
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      points(z.t$size, E_seed, cex=0.2, col="red")
      lines(xx$size, predict(fo@fitFec[[2]], xx, type="response"), col="blue")
    w1 <- Re(eigen(IPM)$vectors[,1]); stable.dist1 <- w1/sum(w1)
    w2 <- Re(eigen(IPM2)$vectors[,1]); stable.dist2 <- w2/sum(w2)
    yl <- range(c(stable.dist1, stable.dist2))
    plot(y, stable.dist1, ylab="", type="l", lwd=2, col="red", ylim=yl,
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    lines(y, stable.dist2, col="blue")
    # plot(y, S.v); points(y, apply(P.mx, 2, sum), col="red", type="l")
    hist(d[[i]]$sizeNext[rcrt.i], main=paste("Recruit sizes:", main.i), 
         xlab="Recruit size (t+1)", col="grey", freq=FALSE)
      xxx <- seq(0, hi*.5, length.out=100)
      rcrt.z <- d[[i]]$sizeNext[is.na(d[[i]]$size) & !is.na(d[[i]]$sizeNext)]
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red", lwd=2)
      lines(xxx, dnorm(xxx, mean(rcrt.z), sd(rcrt.z)), col="blue")
  }
  if(ipmPlots) {
    par(mfrow=c(2,2), mar=c(4,4,2,1)); main.i <- paste("Cell", i)
    if(length(y) != nrow(IPM)) {
      x <- c(0, y)
    } else {
      x <- y
    }
    # sens.mx <- sens(IPM2); elas.mx <- elas(IPM2)
    sens.mx <- sens(IPM); elas.mx <- elas(IPM)
    image.plot(x, x, t(IPM), main=main.i, xlab="Size (t)", ylab="Size (t+1)")
      points(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2))
      abline(a=0, b=1, col="white", lty=2)
    image.plot(P.mx2@meshpoints, P.mx2@meshpoints, t(IPM2), 
               main=main.i, xlab="Size (t)", ylab="Size (t+1)")
      points(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2))
      abline(a=0, b=1, col="white", lty=2)
    image.plot(x, x, t(sens.mx),
               main=paste("Sens:", main.i), xlab="Size (t)", ylab="Size (t+1)")
    image.plot(x, x, t(elas.mx),
               main=paste("Elas:", main.i), xlab="Size (t)", ylab="Size (t+1)")
  }
  if(i %% 100 == 0) cat("Finished cell", i, "\n")
}
lam.df <- env.df %>% add_column(lambda=lambdas, lambda2=lambdas2)
ggplot(lam.df, aes(x=x, y=y, fill=log(lambdas))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", 
                       midpoint=0, limits=log(range(c(lambdas, lambdas2))))
ggplot(lam.df, aes(x=x, y=y, fill=log(lambdas2))) + geom_tile() +
  scale_fill_gradient2(low="darkblue", mid="white", high="darkred", 
                       midpoint=0, limits=log(range(c(lambdas, lambdas2))))
par(mfrow=c(2,2))
plot(log(lambdas) ~ temp, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambdas) ~ prec, data=lam.df); abline(h=0, col="red", lty=2)
plot(log(lambdas), log(lambdas2)); abline(v=0, h=0, a=0, b=1, lty=c(3,2,2))
plot(density(log(lambdas))); abline(v=0, col="red", lty=2)
```
